---
title: "Homelessness"
author: "Winnie Hou"
date: "10/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("dplyr")
library("knitr")
demo <- read.csv("Demographics.csv", stringsAsFactors = FALSE)
length <- read.csv("Length.csv", stringsAsFactors = FALSE)
nop <- read.csv("NumberofPeople.csv", stringsAsFactors = FALSE)
location <- read.csv("Previous_Location.csv", stringsAsFactors = FALSE)
regions <- read.csv("AirbnbRegions1.csv", stringsAsFactors = FALSE)
residency <- read.csv("residency.csv", stringsAsFactors = FALSE)
```

## Questions

**Q1: What is the homeless rate in Seattle as of 2019?**

A: 5,228 people.

```{r 2019_homeless_rate, echo = FALSE}
data <- regions[7,]

data <- data %>% 
  select(Region,X2019.Total.Unsheltered.Persons)

kable(data)

```

**Q2: Has the homeless rate in Seattle increased or decreased over the past 
few years?**

A: The homeless rate in Seattle increased in 2018, but decreased in 2019.
```{r dec_inc, echo=FALSE}
data <- regions[7,]

data <- data %>% 
  select(Region,X2019.Total.Unsheltered.Persons, X2018.Total.Unsheltered.Persons, X2017.Total.Unsheltered.Persons)

kable(data)

```

**Q3: What is the demographic of homelessness in the Seattle area?**

A: The demographic of homelessness in the Seattle area is showed in the table 
below. 27% of the homelessness are between 41 to 50 years old.

```{r demographic, echo=FALSE}
kable(demo)

```

**Q4: Currently, where do homeless people usually stay?**

A: 84% of homelessness live in King County.

```{r residency, echo=FALSE}
kable(residency)

```
